On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-04 main.tex
Updated Section 7 - Noether N

There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $D^{?}$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.

@@

Section 8 is devoted to proving Theorem 8.1. It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}$ for a generic change of variables. The new contribution is in upper bounding the degree of $\Delta_3.$

@@

Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 8.2. Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$

@@

\Xi_i := V(h_i,\hdots,h_n), 

@@

and we obtain a bound on the degree of $\Xi_i$ by applying Bezout's theorem. Hence, if $A\in \Q^{n^2}-\Xi_i$ then

@@

We can apply B\'ezout and obtain

@@

    \deg \Xi_i = \deg V(h_i,\hdots,h_n)
    &\leq \prod_{j=i}^n \deg h_j\\
    &\leq  \prod_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n-i+1}\\
    &\leq  \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n}.

@@

And therefore, by another application of B\'ezout, 

@@

    \deg& \Delta_3 \leq \prod_{i=1}^n \deg \Xi_i\\
    &\leq \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)^{n^2},
    &(=D^{O(n^3 \log n)}\textrm{?})

>>>>

There exists a hypersurface $\Delta_3 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in\{1,\hdots,n\}, f^A$ satisfies $\textbf{H}_i'(7)$.

@@

Section 7 is devoted to proving Theorem 7.1. It has already been shown in \cite{EMP} that $f^A$ satisfies $\textbf{H}_i^{'}(7)$ for a generic change of variables. The new contribution is in upper bounding the degree of $\Delta_3.$

@@

Let $P_{j} \in \mathbb{Q}(\frak{A})[\Xb_{\leq i-1}][T]$ be as in the proof of Proposition 7.2. Since $P_{j}(X_j) \in\I^{\A}= \langle f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n} \rangle,$

@@

\Xi_i := \bigcup_{j=i}^n V(h_j) =V\left(\prod_{j=i}^n h_j \right), 

@@

and we obtain a bound on the degree of $\Xi_i$ by observing that
\deg \Xi_i \leq \sum_{j=i}^n \deg h_j.
Hence, if $A\in \Q^{n^2}-\Xi_i$ then

@@

Now we obtain

@@

    \deg \Xi_i 
    &\leq \sum_{j=i}^n \deg h_j\\
    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .

@@

And therefore,  

@@

    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
